%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Bioinformatician} % Job title
    {\href{http://www.virology.uct.ac.za/vir/research/hiv-diversity-group}{HIV Diversity group, Division of Medical Virology, Department of Pathology}} % Organization
    {University of Cape Town, South Africa} % Location
    {Oct. 2018 - Dec. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Maintained and extended a web app used to manage blood sample storage and related information, written in Django Python web framework.
Dockerized the web app in order to ease reproducing the development environment and simplifying the deployment to production.}
        \item {Wrote data processing pipeline in Julia and Python programming languages for long read Pacbio DNA sequences.}
        \item {Assisted in machine learning project proposal. Explored data in Orange, a data-mining tool. Prepared data using Pandas, encoded data, applied
feature-scaling and feature-selection, performed principal component analysis}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Backend Engineer} % Job title
    {\href{https://opendna.ai}{OpenDNA}} % Organization
    {Cape Town, South Africa} % Location
    {May. 2017 - Oct. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Responsible for deploying and maintaining cloud infrastructure on Amazon AWS, including: Elasticsearch search engine Cluster, Centralized and highly available logging system, where micro-services sent logs to a real-time data processing platform (Kinesis) to be
processed by Logstash, Apache Storm, a distributed realtime computation system, OpenVPN, to allow access to internal services to remain private}
        \item {Encouraged team to adopt a DevOps culture, making operations tasks a shared and automated process where possible
Team members were enabled to submit build automation features and fixes via source-control rather than handing off to an ops team
Containerization of micro-services using Docker simplified configuration and allowed developers to simulate the production environment
more closely}
        \item {Developed CLI tools, frameworks and scripts in Python
Developed an automated API testing framework using pytest library
Created a reporting dashboard with automatic Jira issue handling dependent on deployments status. This allowed QA to know which issues
were present in the current build.
Developed API endpoints and appropriate level of functional tests to guard against regression
Developed database clean up and various other scripts to ensure once-off tasks were carried out effectively}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Quality Assurance Engineer} % Job title
    {\href{https://www.voss-solutions.com}{VOSS}} % Organization
    {Cape Town, South Africa} % Location
    {Jul. 2015 - May. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Managed automated test coverage, continuous integration (CI) and delivery (CD), extending Python based in-house framework with functionality as required}
        \item {Took charge instilling a team discipline with regards to source control (git) merge strategies and treatment of virtual machines as ephemeral. This eliminated the possibility of unreproducible tweaks to dev machines and therefore greater productivity}
        \item {Mentored an intern with little technical background, who proceeded to secure a permanent position in the QA team (remained in position for over 2 years)}
        \item {While on the Cisco integration team, I solved compatibility issues of GNU/Linux users using Webex to connect to meetings, by building and hosting a Docker container \href{https://hub.docker.com/r/dnk8n/docker-webex}{(hosted on Dockerhub)}}
        \item {Managed staging environments which enabled developers to run and contribute to automated tests independently, this distributed a fair portion of QA amongst the team, speeding up overall delivery}
        \item {Gained technical knowledge of the Microsoft Skype for Business and Exchange products, often approached for insight, while on the Microsoft integration team}
        \item {Executed load testing of UC Analytics platform, using JMeter and reported with Pandas and MatPlotLib Python libraries, the insights lead to many performance problems being fixed before delivery}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Transport Engineer} % Job title
    {\href{http://trafficon.co.za}{Trafficon}} % Organization
    {Cape Town, South Africa} % Location
    {Aug. 2014 - Jul. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Produced road traffic micro-simulation models (using PTV Vissim)}
        \item {Learned Python to build bespoke logic into model, allowing simulation of \href{https://www.youtube.com/watch?v=RjTvDzyl8WA}{minibus departure} and indoor multi-story parking systems}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
